---
output: html_document
---

## TDC

```{r, echo=FALSE, message=FALSE}

library(quantmod)

prices <- round(getSymbols("TDC", auto.assign = FALSE), 2)
close <- Cl(last(prices))
open <- Op(last(prices))
```

```{r}
library(magrittr)
library(highcharter)
highchart() %>% 
  hc_title(text = "Scatter chart with size and color") %>% 
  hc_add_serie_scatter(mtcars$wt, mtcars$mpg,
                       mtcars$drat, mtcars$hp)
```

The stock closed ? at ? dollars per share yesterday.

## Price History

The chart below is made with the `quantmod` R package, a widely used package for collecting and visualizing financial data in R. You can learn more about `quantmod` at the [website](http://www.quantmod.com/).

***
  
```{r echo=FALSE}
chartSeries(prices, theme = chartTheme("white", bg.col = "white"))
```

## Raw Data

The table below displays the daily price data for the stock. In the next section, we will learn how to make a concise, interactive table with the `DT` package, a new package for making searchable data tables. You can learn more about the `DT` package at the website 

***
  
```{r echo=FALSE}
DT::datatable(data.frame(prices[, 1:4], 2))
```
